---
title: "READIE_Ploting_Scripts"
author: "Santiago Morales, Wenyi Xu"
date: "04/29/2024"
output:
  html_document:
    toc: true
    fig_height: 8.5
    fig_width: 12
    css: custom 2.css
editor_options: 
  chunk_output_type: console
---
This script generates plots based on the READIE toolbox and reads in the outputs of the toolbox. This version aligns with the tutorial found at:  https://github.com/Bead-Lab/The-READIE-Toolbox-Reliability-Effect-size-And-Data-quality-In-EEG

Please cite: 
Xu, W., Monachino, A. D., McCormick, S., Margolis, E. T., Sobrino, A., Bosco, C., Franke, C., Davel, L., Zieff, M. R., Donald, K. A., Gabard-Durnam, L. J., & Morales, S. (under review). Advancing the Reporting of Developmental EEG Data: Tools for Estimating Reliability, Effect Size, and Data Quality Metrics.

Any questions or bugs, please post on Github or email: Wenyi (Echo) Xu (wenyix@usc.edu) or Santiago Morales (santiago.morales@usc.edu)

# Setup
```{r eval=TRUE, echo=T, message=FALSE, warning=FALSE, results='hide', fig.show='hide'}
list.of.packages <- c("psych","ggplot2", "dplyr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
# Loading packages
lapply(list.of.packages, require, character.only = TRUE)

# Setting suggested plotting options
my_opts <- list(theme_classic() + theme(axis.text=element_text(size=14), axis.title=element_text(size=15,face="bold"), legend.title=element_text(size=14,face="bold"), legend.text=element_text(size=13), strip.text.x = element_text(size = 14, face="bold")))
setwd("...READIE_Toolbox_0611/results") # Update this part to READIE Output Results Folder 

############################################################
```

# VEP
## SME VEP
### N1
```{r}
dfm <- read.csv("Mean Amplitude for Window 75-130/SME_triallevel.csv")
(p.n1.sme <- ggplot(dfm, aes(x =cond,y=aSEM, fill = cond)) +
  stat_summary(fun.y = mean, geom = "bar", position=position_dodge(width=0.95), alpha = .7) + 
  geom_point(aes(colour=cond), size=1, position = "jitter", alpha = .4) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=.3, position=position_dodge(width=0.95)) +
  my_opts + labs(y = expression("Standardized Measurement Error")) + 
  theme(legend.position="none") + ggtitle("N1 VEP Task") )

# Note that this task does not have a meaningful condition variable. Feel free to change that so it best fit your study! 
```

### P1
```{r}
dfm <- read.csv("Mean Amplitude for Window 100-230/SME_triallevel.csv")


(p.p1.sme <- ggplot(dfm, aes(x =cond,y=aSEM, fill = cond)) +
  stat_summary(fun.y = mean, geom = "bar", position=position_dodge(width=0.95), alpha = .7) + 
  geom_point(aes(colour=cond), size=1, position = "jitter", alpha = .4) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=.3, position=position_dodge(width=0.95)) +
  my_opts + labs(y = expression("Standardized Measurement Error")) + 
  theme(legend.position="none") + ggtitle("P1 VEP Task") )

# Note that this task does not have a meaningful condition variable. Feel free to change that so it best fit your study! 
```

## Plotting all together
```{r}
library(ggpubr)
ggsave("VEP_SME_Example_Fig.jpg", ggarrange(p.n1.sme, p.p1.sme, ncol=1, nrow=2, common.legend = FALSE, legend="none",labels = c("A", "B"), font.label = list(size = 18, face = "bold")), width = 7, height = 14, units = 'in', dpi = 150)

```

# Effect Size
## Eff VEP Overall
### N1
```{r}
df.n1 <- read.csv("Mean Amplitude for Window 75-130/eff_summary_overall.csv")

# Plotting the data
p.n1.eff <- ggplot(df.n1, aes(x = cond_s, y = mean, fill = cond_s)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.95), alpha = 0.7) +
  geom_errorbar(aes(ymin = lower_pct, ymax = upper_pct), width = 0.2) +
  labs(x = "Condition", y = expression("Effect Size (Cohen's d)")) +
  theme(legend.position = "none") +
  ggtitle("N1 Effect Size") +
  scale_fill_manual(values = c("#990000", "gray", "orange")) +
  scale_color_manual(values = c("#990000", "gray", "orange"))

# Display the plot
print(p.n1.eff)

```

### P1
```{r}
df.p1 <- read.csv("Mean Amplitude for Window 100-230/eff_summary_overall.csv")
p.p1.eff <- ggplot(df.p1, aes(x = cond_s, y = mean, fill = cond_s)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.95), alpha = 0.7) +
  geom_errorbar(aes(ymin = lower_pct, ymax = upper_pct), width = 0.2) +
  labs(x = "Condition", y = expression("Effect Size (Cohen's d)")) +
  theme(legend.position = "none") +
  ggtitle("N1 Effect Size") +
  scale_fill_manual(values = c("#990000", "gray", "orange")) +
  scale_color_manual(values = c("#990000", "gray", "orange"))

# Display the plot
print(p.p1.eff)
```

## Plotting all together
```{r}
library(ggpubr)
ggsave("VEP_Eff_Overall_Example.jpg", ggarrange(p.n1.eff, p.p1.eff, ncol=1, nrow=2, common.legend = FALSE, legend="none",labels = c("N1", "P1"), font.label = list(size = 18, face = "bold")), width = 7, height = 14, units = 'in', dpi = 150)
```

## Eff VEP Trial-level
### N1
```{r}
df.n1 <- read.csv("Mean Amplitude for Window 75-130/eff_summary_triallevel.csv")
df.n1$n_trials <- as.numeric(sapply(strsplit(df.n1$cond_s,"_"), `[`, 2))
p.n1.eff.trial <- ggplot(df.n1, aes(x = n_trials, y = mean)) +
    geom_errorbar(aes(ymin = lower_pct, ymax = upper_pct), width = .2) +
    geom_line() + geom_point()+
    scale_x_continuous(limits = c(9, 101), breaks = seq(10, 90, by = 10)) +
    theme(legend.position = "bottom") +
    labs(x = "Number of Trials", y = expression("Effect Size (Cohen's d)")) +
    ggtitle("N1") +
    scale_fill_manual(values = c("#990000", "gray50", "orange")) +
    scale_color_manual(values = c("#990000", "gray50", "orange"))
print(p.n1.eff.trial)
```

### P1
```{r}
df.p1 <- read.csv("Mean Amplitude for Window 100-230/eff_summary_triallevel.csv")
df.p1$n_trials <- as.numeric(sapply(strsplit(df.p1$cond_s,"_"), `[`, 2))
p.p1.eff.trial <- ggplot(df.p1, aes(x = n_trials, y = mean)) +
    geom_errorbar(aes(ymin = lower_pct, ymax = upper_pct), width = .2) +
    geom_line() + geom_point()+
    scale_x_continuous(limits = c(9, 101), breaks = seq(10, 90, by = 10)) +
    theme(legend.position = "bottom") +
    labs(x = "Number of Trials", y = expression("Effect Size (Cohen's d)")) +
    ggtitle("P1") +
    scale_fill_manual(values = c("#990000", "gray50", "orange")) +
    scale_color_manual(values = c("#990000", "gray50", "orange"))
print(p.p1.eff.trial)
```

## Plotting all together
```{r}
library(ggpubr)
ggsave("VEP_Eff_TrialLevel_Example.jpg", ggarrange(p.n1.eff.trial, p.p1.eff.trial, ncol=1, nrow=2, common.legend = FALSE, legend="bottom",labels = c("N1", "P1"), font.label = list(size = 18, face = "bold")), width = 10, height = 14, units = 'in', dpi = 150)
```

# Reliability
## Rel VEP Overall
## Rel VEP Trial-level
## Given that there are only 5 participants in the sample dataset, the reliability for both N1 and P1 component is negative. Please refer to the effect size plotting script.
